---
title: "Lab 6"
author: "Divyanshu Kawankar"
date: "10/17/2021"
output: pdf_document
---

Questions to Answer:

>Q1. Write a function grade() to determine an overall grade from a vector of student homework assignment scores dropping the lowest single score. If a student misses a homework (i.e. has an NA value) this can be used as a score to be potentially dropped. Your final function should be adquately explained with code comments and be able to work on an example class gradebook such as this one in CSV format: “https://tinyurl.com/gradeinput” [3pts]

```{r}
plot(1:10)
```


```{r}
# Example input vectors to start with
student1 <- c(100, 100, 100, 100, 100, 100, 100, 90)

student2 <- c(100, NA, 90, 90, 90, 90, 97, 80)

student3 <- c(90, NA, NA, NA, NA, NA, NA, NA)
```


```{r}
#First find mean
student1 <- c(100, 100, 100, 100, 100, 100, 100, 90)

mean(student1)
```

```{r}
#identify student1 lowest score

min(student1)
```

```{r}
#which element is the lowest

which.min(student1)
```

```{r}
#lowest score for student 1

student1[which.min(student1)]
```

```{r}
#Use (-) to drop the value

student1[-which.min(student1)]
```

```{r}
#Now we can find the mean with the lowest score dropped

mean(student1[-which.min(student1)])
```

```{r}
#Repeat with student 2

student2[-which.min(student2)]
```

```{r}
#Because of the NA, we could not figure out the product

#We need to remove the NA elements of the student2 vector

mean(student2[ -which.min(student2)], na.rm = TRUE)
```

```{r}
#We can try it again with Student 3

student3

mean(student3[-which.min(student3)], na.rm = TRUE)
```

```{r}
#As a result, we can replace NA with 0, for example with student 2
```


```{r}
is.na(student2)
```

```{r}
#The true represents where a NA exists, so to find the position

which(is.na(student2))
```

```{r}
#Now lets make NA values into 0
student.prime <- student2

student.prime[which(is.na(student.prime))] = 0

student.prime
```

```{r}
#given this, the mean is

student.prime <- student2
student.prime[ which(is.na(student.prime)) ] = 0
mean(student.prime[ -which.min(student.prime) ])
```

```{r}
#Repeat for student 3

student.prime <- student3
student.prime[ which(is.na(student.prime)) ] = 0
mean(student.prime[ -which.min(student.prime) ])
```

```{r}
#Simplify

x <- student3
x[ which(is.na(x)) ] = 0
mean(x[ -which.min(x) ])
```

```{r}
#Create a body of functions using the given grade

grade <- function(x) {
  x <- as.numeric(x)
  x[ which(is.na(x)) ] = 0
mean(x[ -which.min(x) ])}

grade(student2)
```

```{r}
#use given file in lab ws

scores <- read.csv("https://tinyurl.com/gradeinput", row.names=1)

scores
```

```{r}
#Turn NA input into numeric values

grade(as.numeric(scores[10,]))

is.numeric(scores[10,])
```

```{r}
#Now grade all students using the apply function

ans <- apply(scores,1,grade)

ans
```

>Q2. Using your grade() function and the supplied gradebook, Who is the top scoring student overall in the gradebook? [3pts]

```{r}
#Top overall scoring student in gradebook

which.max(ans)
```

>Q3. From your analysis of the gradebook, which homework was toughest on students (i.e. obtained the lowest scores overall? [2pts]

```{r}
#We can use the apply() function over the columns by setting the margin=2 argument.

apply(scores,2,mean, na.rm=TRUE)
```
